New Insights on the Role of Context in the Perception of a Human-like Robot

### 2015-04-20 main.tex
Improved abstract, added stub on 'Context and Interaction Design'

\author{
Ashish Ranjan Jha, Kshitij Sharma, Séverin Lemaignan, Pierre Dillenbourg\\
CHILI Lab, École Polytechnique Fédérale de Lausanne\\
\url{firstname.lastname@epfl.ch}
}

@@

What leads us to attribute human-like characteristics to robots? The physical
appearance of the robot, as well as the design of the behaviours, certainly play a key
role. This paper however evidences another mechanism at play, more subtle and partially
unconscious: the \emph{cognitive context}\fxwarning{cognitive context, really?}
of the interaction.

@@

\begin{inparaenum}[\itshape a\upshape)]
As a result, we show that \item gaze patterns correlate with post-hoc anthropomorphic
attributions, and hence, eye-tracking can be used as a novel \emph{in-the-moment}
metric of anthropomorphism, \item fixations on the robot's head are a good
predictor of anthropomorphic attributions, \item simple context priming is sufficient
to elicit significantly different anthropomorphic attributions.
\end{inparaenum}

This last item has noteworthy implications regarding the design of human-like human-robot
interactions, and we propose to discuss them at the end of the article.

@@

>>>>

\author{
Séverin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre Dillenbourg\\
CHILI Lab, École Polytechnique Fédérale de Lausanne\\
\url{firstname.lastname@epfl.ch}
}

@@

What leads us to attribute human-like characteristics to robots? The physical
appearance of the robot and the design of its behaviours do obviously play a key
role. This paper however evidences another mechanism at play, more subtle and partially
unconscious: the context of the interaction, and more precisely, the cognitive
prerequisites that the interaction presupposes.

@@

\begin{inparaenum}[\itshape a\upshape)]
As a result, we show that \item specific gaze patterns (fixations on the head of
the robot) correlate with post-hoc anthropomorphic
attributions, and hence, eye-tracking can be used as a novel \emph{in-the-moment}
metric of anthropomorphism, and \item simple context priming is sufficient
to elicit significantly different anthropomorphic attributions.
\end{inparaenum}

This second point has important implications regarding the design of human-like human-robot
interactions, and we propose to discuss them at the end of the article.

@@

\subsection{Context and Interaction Design}

\fxwarning{discuss here how context can be used to shape the interaction}
